### 2018-02-06 docs/paper.tex
plane wave decomposition

>>>>

\subsection{Projection of Pseudowavefunctions onto Partial Waves}

\begin{equation}
e^{i\mathbf{k} \cdot \mathbf{r}} = 4\pi \sum_{l=0}^{\infty}\sum_{m=-l}^{l}
i^l j_l(kr)Y_l^{m*}(\mathbf{\hat{k}})Y_l^m(\mathbf{\hat{r}})
\label{eq:pwexp}
\end{equation}
$\mathbf{r_A} = \mathbf{r} - \mathbf{R_A}$, $\phi_i(\mathbf{r})=R_i(r)Y_l^m(\mathbf{\hat{r}})$,
$\widetilde{\phi}_i(\mathbf{r})=\widetilde{R}_i(r)Y_l^m(\mathbf{\hat{r}})$,
$\mathbf{k'}=\mathbf{k}+\mathbf{G}$\\
$$\widetilde{\psi}_{n\mathbf{k}}=\frac{1}{\sqrt{V}}\sum_{\mathbf{G}}
C_{n\mathbf{k}\mathbf{G}}e^{i\mathbf{k'}\cdot \mathbf{r}}$$
$$\widetilde{\psi}_{n\mathbf{k}}=\frac{4\pi}{\sqrt{V}}\sum_{\mathbf{G}}
C_{n\mathbf{k}\mathbf{G}}\sum_{l=0}^{\infty}\sum_{m=-l}^{l}
i^l j_l(k'r_A)Y_l^{m*}(\mathbf{\hat{k'}})Y_l^m(\mathbf{\hat{r}_A})$$
$$\phi_i(\mathbf{r})\widetilde{\psi}_{n\mathbf{k}}=\frac{4\pi}{\sqrt{V}}\sum_{\mathbf{G}}
C_{n\mathbf{k}\mathbf{G}}\sum_{l'=0}^{\infty}\sum_{m'=-l'}^{l'}
i^{l'} j_{l'}(k'r_A)Y_{l'}^{m'*}(\mathbf{\hat{k'}})Y_{l'}^{m'}(\mathbf{\hat{r}_A})
Y_l^{m*}(\mathbf{\hat{r}}_A)R_i(r_A)$$
$$\braket{\phi_i(\mathbf{r})|\widetilde{\psi}_{n\mathbf{k}}}=
\frac{4\pi i^l}{\sqrt{V}}\sum_{\mathbf{G}} C_{n\mathbf{k}\mathbf{G}}
Y_l^{m*}(\mathbf{\hat{k'}})\int_0^{\infty}drr^2R_i(r_A)j_l(k'r_A)$$
$$\braket{\phi_i-\widetilde{\phi}_i|\widetilde{\psi}_{n\mathbf{k}}}=
\frac{4\pi i^l}{\sqrt{V}}\sum_{\mathbf{G}} C_{n\mathbf{k}\mathbf{G}}
Y_l^{m*}(\mathbf{\hat{k'}})\int_0^{\infty}drr^2R_i(r_A)j_l(k'r_A)$$

After the projection is decomposed into a summation over integrals of spherical
Bessel functions, it can be calculated via spherical Bessel transform. This code
uses the fast spherical Bessel transform method NumSBT developed by Talman.\cite{TALMAN}
It runs in $O(NlnN)$ time and works on a logarithmic grid, making it convenient for use with
the POTCAR representations of the partial waves. The resulting logarithmic k-space
grid can be used to calculate the values of the relevant integrals via interpolation.
